Sterile Neutrinos, a Summary

### 2015-04-15 p3_505/presentation/pres.tex

\begin{frame}
  \frametitle{The LSND Experiment}
  \footnotesize{
    \begin{columns}
      \begin{column}{.5\linewidth}      
        \begin{itemize}
        \item Liquid Scintillator Neutrino Detector.
        \item Los Alamos National Laboratory from 1993 to 1998.
        \item Cherenkov detector using 1220 PMTs.
        \item Protons strike target, use pions decaying at test to product $\overline{\nu}_\mu$.
        \end{itemize}
      \end{column}
      \begin{column}{.5\linewidth}
        \begin{itemize}
        \item $117.9 \pm 22.4$ events, signal excess of $87.9\pm 22.4 \pm 6.0$.
        \item $(\sin^2 2\theta,\Delta m^2)$ fit extracts allowed oscillation regions.
        \item Best fits yields $\Delta m^2 \sim 1$ eV.
        \item Disagrees with solar and atmospheric oscillation experiments and also LEP experiments for 3 light flavor neutrinos.
        \end{itemize}
      \end{column}
    \end{columns}
  }
  \begin{center}
    \includegraphics[width=.35\linewidth]{../figures/LSND_plot.pdf}
  \end{center}
\end{frame}
\begin{frame}
  \frametitle{The MiniBooNE Experiment}
  \scriptsize{
    \begin{columns}
      \begin{column}{.5\linewidth}      
        \begin{itemize}
        \item Developed to answer the LSND anomaly.
        \item Collected data at Fermilab from 2002 to 2012
        \item Cherenkov detector using PMTs (just like LSND)
        \item 8 GeV protons from the Booster strike beryllium target, pions decay producing neutrinos
          \begin{center}
            \includegraphics[width=.9\linewidth]{../figures/miniboone_excess.pdf}
          \end{center}
        \end{itemize}
      \end{column}
      \begin{column}{.5\linewidth}
        \begin{itemize}
        \item Consistent with the LSND anti neutrino oscillation result.
          \begin{center}
            \includegraphics[width=.6\linewidth]{../figures/miniboone_regions.pdf}
          \end{center}
        \item Detector systematics make it difficult to differentiate between $\pi^0\rightarrow\gamma\gamma$ and an electron in the detector.
        \end{itemize}
      \end{column}
    \end{columns}
  }
\end{frame}

@@

\begin{frame}
  \frametitle{The Super-Kamiokande Experiment}
  \begin{itemize}
  \item Atmospheric, TODO experiment
  \item Latest results TODO
    \begin{center}
      \includegraphics[width=.5\linewidth]{../figures/sk1.pdf}
    \end{center}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Daya Bay Experiment}
  \begin{itemize}
  \item Reactor, TODO experiment
  \item Latest results TODO
    \begin{center}
      \includegraphics[width=.5\linewidth]{../figures/daya1.pdf}
    \end{center}
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{The LSND Experiment}
  \footnotesize{
    \begin{columns}
      \begin{column}{.5\linewidth}      
        \begin{itemize}
        \item Liquid Scintillator Neutrino Detector.
        \item Los Alamos National Laboratory from 1993 to 1998.
        \item Cherenkov detector using 1220 PMTs.
        \item Protons strike target, use pions decaying at test to product $\overline{\nu}_\mu$.
        \end{itemize}
      \end{column}
      \begin{column}{.5\linewidth}
        \begin{itemize}
        \item $117.9 \pm 22.4$ events, signal excess of $87.9\pm 22.4 \pm 6.0$.
        \item $(\sin^2 2\theta,\Delta m^2)$ fit extracts allowed oscillation regions.
        \item Best fits yields $\Delta m^2 \sim 1$ eV.
        \item Disagrees with solar and atmospheric oscillation experiments and also LEP experiments for 3 light flavor neutrinos.
        \end{itemize}
      \end{column}
    \end{columns}
  }
  \begin{center}
    \includegraphics[width=.35\linewidth]{../figures/LSND_plot.pdf}
  \end{center}
\end{frame}
\begin{frame}
  \frametitle{The MiniBooNE Experiment}
  \scriptsize{
    \begin{columns}
      \begin{column}{.5\linewidth}      
        \begin{itemize}
        \item Developed to answer the LSND anomaly.
        \item Collected data at Fermilab from 2002 to 2012.
        \item Cherenkov detector using PMTs (just like LSND).
        \item 8 GeV protons from the Booster strike beryllium target, pions decay producing neutrinos.
          \begin{center}
            \includegraphics[width=.9\linewidth]{../figures/miniboone_excess.pdf}
          \end{center}
        \end{itemize}
      \end{column}
      \begin{column}{.5\linewidth}
        \begin{itemize}
        \item Consistent with the LSND antineutrino oscillation result.
          \begin{center}
            \includegraphics[width=.6\linewidth]{../figures/miniboone_regions.pdf}
          \end{center}
        \item Detector systematics make it difficult to differentiate between $\pi^0\rightarrow\gamma\gamma$ and an electron in the detector.
        \end{itemize}
      \end{column}
    \end{columns}
  }
\end{frame}

@@

\begin{frame}
  \frametitle{The Super-Kamiokande Experiment}
  \begin{itemize}
  \item Atmospheric neutrino oscillation experiment, 22.5 kton water Cherenkov detector
  \item Can not measure $\Delta m^{2}_{41}$ in this analysis
  \item Super-K exclusion limits at 90\% (solid) and 99\% (dashed) confidence
  \item Joint analysis of MiniBooNE and SciBooNE (dotted) at 90\% confidence
    \begin{center}
      \includegraphics[width=.5\linewidth]{../figures/sk1.pdf}
    \end{center}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Daya Bay Experiment}
  \begin{itemize}
  \item Reactor antineutrino experiment
  \item Six liquid scintillator/PMTs detectors, six nuclear reactors at different baselines
  \item Sterile neutrino measurements possible at smaller mass squared differences than other experiments, $10^{−3} \text{ eV}^2  \lesssim \left|\Delta m^{2}_{41}\right| \lesssim 0.1 \text{ eV}^2$
    \begin{center}
      \includegraphics[width=.5\linewidth]{../figures/daya1.pdf}
    \end{center}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{(Selected) Future Experiments}
  \begin{itemize}
  \item MicroBooNE: Larger follow up experiment to MiniBooNE
   \begin{itemize}
     \item Time projection chamber with a 60 ton fiducial volume of liquid argon
     \item Will be able to distinguish between photons and electrons
     \item Expected to resolve the MiniBooNE excess anomaly
   \end{itemize}
  \item NOvA: Long baseline experiment using the NuMI beam
   \begin{itemize}
     \item 330 ton near and 14 kton far liquid scintillator detectors located near the surface
     \item Primary physics goals are oscillation measurements, will also perform sterile neutrino measurements
   \end{itemize}
  \end{itemize}
\end{frame}
